Exploring the Presidents Corpus

### 2019-10-16 Source/Paper 1 - Presidents Corpus Paper/PresidentsCorpus.tex
Presidents Corpus - Intro and Method

\section{Results}\label{results}
One of the most important thing to note is the wide variety of samples between the three presidents and also the varying timescales. RR participated in 46 press conferences over eight years (an average of 5.75 a year) which is the fewest number of press conferences given by an American president during their term of office. GHWB participated in 136 press conferences over four years (an average of  34 a year) and DJT participated in 29 press conferences to date (an average of 19.3 per year). Equally, there are variances in the average number of words. RR produced an average of 3424 words per conference compared to 2608 by GHWB (unpaired t = 4.434, p\textless 0.001) and DJT at 1849 words (unpaired t = 6.524, p\textless 0.001).
\begin{table}[H]
	\begin{center}
	\begin{tabular}{ | p{3cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} |}
		\hline
		& RR & GHWB & DJT \\ \hline
		Total Words & 3423.91 (416.42) & 2607.72 (1210.38) & 1848.65 (1549.38) \\ \hline
		Unique Words & 894.13 (85.15) & 667.76 (218.67) & 481.82 (221.29) \\ \hline
		Non Specific Nouns & 12.72 (4.63) & 6.78 (4.32) & 7.41 (8.75) \\ \hline
		LI Verbs & 124.22 (17.89)& 103.45 (51.87) & 84.48 (75.78) \\ \hline
	\end{tabular}
	\caption{\label{tab:table-name}Means and Standard Deviations of important features}
	\end{center} 
\end{table}

@@

\begin{table}[H]
	\begin{center}
	\begin{tabular}{ | p{3cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} |}
		\hline
		& RR v GHWB & RR v DJT & GHWB v DJT \\ \hline
		Total Words & \textbf{4.434***} & \textbf{6.524***} & \textbf{2.899**} \\ \hline
		Unique Words & \textbf{6.832***} & \textbf{11.403***} & \textbf{4.137***} \\ \hline
		Non Specific Nouns & \textbf{7.877***} & \textbf{3.426**} & -0.574 \\ \hline
		LI Verbs & \textbf{2.656**} & \textbf{3.420***} & 1.628 \\ \hline
		\multicolumn{4}{@{}p{1.5in}}{\footnotesize * denotes p\textless 0.05} \\
		\multicolumn{4}{@{}p{1.5in}}{\footnotesize ** denotes p\textless 0.01} \\
		\multicolumn{4}{@{}p{1.5in}}{\footnotesize *** denotes p\textless 0.001} \\
	\end{tabular}
	\caption{\label{tab:table-name}RR T-tests vs GWB and DJT}
	\end{center} 
\end{table}

>>>>

\section{Results}\label{results}
One of the most important thing to note is the wide variety of samples between the three presidents and also the varying timescales. RR participated in 46 press conferences over eight years (an average of 5.75 a year) which is the fewest number of press conferences given by an American president during their term of office. GHWB participated in 136 press conferences over four years (an average of 34 a year) and DJT participated in 29 press conferences to date (an average of 19.3 per year). Equally, there are differences in the average number of words. RR produced an average of 3424 words per conference compared to 2608 by GHWB (unpaired t = 4.434, p\textless 0.001) and DJT at 1849 words (unpaired t = 6.524, p\textless 0.001).
\begin{table}[H]
	\begin{center}
	\begin{tabular}{ | p{3cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} |}
		\hline
		& RR & GHWB & DJT \\ \hline
		Total Words & 3423.91 (416.42) & 2607.72 (1210.38) & 1848.65 (1549.38) \\ \hline
		Unique Words & 894.13 (85.15) & 667.76 (218.67) & 481.82 (221.29) \\ \hline
		Mean Length of Utterance & 23.17 (1.402) & 18.71 (2.067) & 481.82 (221.29) \\ \hline
		Non Specific Nouns & 12.72 (4.63) & 6.78 (4.32) & 7.41 (8.75) \\ \hline
		LI Verbs & 124.22 (17.89)& 103.45 (51.87) & 84.48 (75.78) \\ \hline
	\end{tabular}
	\caption{\label{tab:table-name}Means and Standard Deviations of important features}
	\end{center} 
\end{table}

@@

\begin{table}[H]
	\begin{center}
	\begin{tabular}{ | p{3cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} |}
		\hline
		& RR v GHWB & RR v DJT & GHWB v DJT \\ \hline
		Total Words & \textbf{4.434***} & \textbf{6.524***} & \textbf{2.899**} \\ \hline
		Unique Stems & \textbf{10.878***} & \textbf{10.111***} & \textbf{4.148***} \\ \hline
		Mean Length of Utterance & \textbf{16.175***} & \textbf{25.084***} & \textbf{13.484***} \\ \hline	
		Non Specific Nouns & \textbf{7.877***} & \textbf{3.426**} & -0.574 \\ \hline
		LI Verbs & \textbf{2.656**} & \textbf{3.420***} & 1.628 \\ \hline
		\multicolumn{4}{@{}p{1.5in}}{\footnotesize * denotes p\textless 0.05} \\
		\multicolumn{4}{@{}p{1.5in}}{\footnotesize ** denotes p\textless 0.01} \\
		\multicolumn{4}{@{}p{1.5in}}{\footnotesize *** denotes p\textless 0.001} \\
	\end{tabular}
	\caption{\label{tab:table-name}RR T-tests vs GWB and DJT}
	\end{center} 
\end{table}
